TODO

1. describe work at mpi v
2. describe phd v
8. get list of conference presentations
5. Software: Add LoanPy. copiusapi. maybe sth third? v
3. Add erasmus paris to BA
4. bullet to phd: stay in Finland
6. CIFU, stuts, ifusco vienna, winterschool vienna
7. fix "presenting author"
9. Finland, Erasmus+
10. put languages
11. copy from old cv, add r, check keywords

%last. Send another e-mail to grammarly and ask

keywords: simulation modelling. uncovering neglected histories. multilingualism. comparative analysis, interdisciplinary, NHL, reconstruct, explain, understand, causality, qualitative, quantitative and experimental methods, generative simulation models of the dynamics of historical and contemporary multilingualism, historical and present day data, informal models from published literatures in linguistics, historical inference on population dynamics; the use of in-development software designed for generative micro-simulation, stand-alone modular add-ons to these software environments specific to multi-linguistic phenomena. qualitative arguments (informal models) into modeling assumptions for use in either micro or macro-simulation projects. generative (forward) simulation and inference methods, demonstrated problem-solving ability, both historically and in contemporary contexts,

\cvsection{Organised Conferences}\\
\begin{cvpubs}
    \cvpub{CIFU}
\end{cvpubs}

\begin{cvpubs}
    \cvpub{Stuts}
\end{cvpubs}

\begin{cvpubs}
    \cvpub{CIFU Online}
\end{cvpubs}

\begin{cvpubs}
    \cvpub{IFUSCO}
\end{cvpubs}

\begin{cvpubs}
    \cvpub{INFUSE Winter school}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {CIFU 2022}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {StuTS 2021}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {IFUSCO 2019}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {INFUSE 2018}
\end{cvpubs}

{Public Presentation University of Vienna} % Award
    {Formalising manual workflows} % Awarding Organization
    {pseudo-code} % Amount -- leave blank if not including amounts
    {2019} % Date(s)
    
    \cvhonor
    {Presentation PhD seminar University of Helsinki} % Award
    {Converting pseudo-code to a collection of scripts} % Awarding Organization
    {Prototype} % Amount -- leave blank if not including amounts
    {2020} % Date(s)

    \cvhonor
    {Deutsche Gesellschaft} % Award
    {Converting scripts to re-usable functions, architecture, modules} % Awarding Organization
    {Version 1} % Amount -- leave blank if not including amounts
    {2021} % Date(s)