%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\begin{small}\textit{* as Presenter}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub {January 7, 2025. \textit{Computer-assisted methods for the detection/evaluation of ancient loanwords}. Seminar series Introduction to Historical-Comparative Finno-Ugric Studies, University of Vienna.}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {April 11, 2024. \textit{Yukaghir loanwords in Uralic? Evidence for and against ancient contact}. Seminar series Linguistic Typology and Language Universals, Friedrich Schiller University Jena, Germany.}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {September 6, 2023. \textit{Inferring language contact through rule-based computational borrowing detection}. Interdisciplinary Seminar Series on Human Diversity, Turku, Finland.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub{\textbf{Viktor Martinovi{\'c}}, Tihomir Rangelov*. July 12, 2023. \textit{Automatic detection of phonological adjustments in Bislama’s lexicon of English origin}. Vanuatu Languages Conference, Port Vila, Vanuatu.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Participation}

\begin{cvpubs}
    \cvpub {July 23–28, 2019. 10th Global WordNet Conference, Wroclaw, Poland}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Conference Presentations}

\begin{cvpubs}
    \cvpub {August 21–26, 2022, \textit{Gothic loanwords in Hungarian? A case study of computer-assisted borrowing detection}. Congressus XIII Internationalis Fenno-Ugristarum, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {November 12–20, 2021, \textit{Workshop: \textipa{f@nEtIk tr\ae nskraIb@rz In "paIT@n}. From orthography to IPA}. 70th Student Conference on Linguistics, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {September 23–24, 2021. \textit{Rule-based vs. machine learning models in automated borrowing detection}. The Seventh International Workshop on Computational Linguistics of Uralic Languages, Syktyvkar, Russia}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {September 6–8, 2021. \textit{loanpy – a framework for computer-aided borrowing detection}. Protolang 7, Düsseldorf, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {February 23–26, 2021. \textit{Loanpy: A framework for computer-aided borrowing detection}. 43rd Annual Conference of the German Society for Linguistics, Freiburg, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {November 19–22, 2020. \textit{Towards a computer-aided framework for borrowing detection: Gothic loanwords in Hungarian?} 68th StuTS, Berlin, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {August 17–19, 2020, \textit{Gothic-Hungarian lexical contacts}. Pre-Congress of Congressus XIII Internationalis Fenno-Ugristarum, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {July 1, 2019, \textit{Gothic loanwords in Hungarian? Computational approaches to borrowing detection}. Faculty-wide presentation at Dies Doctoralis of the Faculty of Philological and Cultural Studies, University of Vienna, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {June 6–8, 2019, \textit{Hungaro-Gothica: Are there Gothic loanwords in Hungarian?} 3rd Budapest Linguistics Conference, Budapest, Hungary}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {May 9–10, 2019, \textit{Hungarian-Gothic contact?} Workshop of Linguistics Doctoral Students of Vienna German Studies and Friends, Vienna, Austria}
\end{cvpubs}

%-------------------------------------------------------------------------------

