%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {University of Vienna, Finno-Ugrian Department} % Degree
    {PhD Computational Evolutionary Linguistics} % Institution
    {Vienna, Helsinki, Reykjavík, Leipzig} % Location
    {October 2018 - ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Thesis on automated approaches to the detection of ancient loanwords.}
        \item{Training, evaluating and comparing LLMs, RNNs, and rule-based predictive models.}
        \item{Extracting, standardising, storing and maintaining multifaceted linguistic data.}
        \item{Research stays in Helsinki (2019/20), Reykjavík (2021/22), and Leipzig (2022/23).}
      \end{cvitems}
    }

  \cventry
    {University of Vienna, Finno-Ugrian Department} % Degree
    {MA Finno-Ugrian Studies (Ø 1.5)} % Institution
    {Vienna} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis on manual detection of Germanic loanwords in Hungarian.}
      \end{cvitems}
    }

  \cventry
    {Vienna School of International Studies / Diplomatische Akademie} % Degree
    {Diploma in International Relations} % Institution
    {Vienna} % Location
    {October 2017 - June 2018} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
        \item{International law and EU law.}
        \item{Microeconomics and macroeconomics.}
        \item{History, political science, and international relations.}
      \end{cvitems}
    }
    
  \cventry
    {University of Vienna, Finno-Ugrian Department} % Degree
    {BA Hungarian Studies (Ø 1.6)} % Institution
    {Vienna \& Paris} % Location
    {2014 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis on the history of Germanic loanwords in Hungarian.}
      \end{cvitems}
    }
        
  \cventry
    {Pannonhalma Secondary School} % Degree
    {A-levels with distinction (Ø 1.1)} % Institution
    {Hungary} % Location
    {2011 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Subjects: Hungarian Language and Literature, Mathematics, History, English, German, Geography.}
        \item{Language of exams: Hungarian.}
      \end{cvitems}
    }

  \cventry    
    {Schottengymnasium} % Degree
    {Secondary Education} % Institution
    {Vienna} % Location
    {2005 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Strong focus on languages.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
