%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\begin{small}\textit{* presenting author}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub {6 September 2023. \textit{Inferring language contact through rule-based computational borrowing detection}. Interdisciplinary human diversity seminar series, Turku, Finland.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub{\textbf{Viktor Martinovi{\'c}}, Tihomir Rangelov*. 12 July 2023. \textit{Automatic detection of phonological adjustments in Bislama’s lexicon of English origin}. Vanuatu Languages Conference, Port Vila, Vanuatu.}
\end{cvpubs}

\cvsubsection{Attendance}

\begin{cvpubs}
    \cvpub {23-28 July 2019. 10th Global WordNet Conference, Wroclaw, Poland}
\end{cvpubs}
%-------------------------------------------------------------------------------
\pagebreak
\cvsubsection{Conference Presentations}

\begin{cvpubs}
    \cvpub {21-26 August 2022, \textit{Gothic loanwords in Hungarian? A case study of computer-assisted borrowing detection}. Congressus XIII Internationalis Fenno-Ugristarum, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {12-20 November 2021, \textit{Workshop: \textipa{f@nEtIk tr\ae nskraIb@rz In "paIT@n}. From orthography to IPA}. 70. Studentische Tagung Sprachwissenschaft, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {23-24 September 2021. \textit{Rule-based vs. machine learning models in automated borrowing detection}. The Seventh International Workshop on
Computational Linguistics of Uralic Languages, Syktyvkar, Russia}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {6-8 September 2021. \textit{loanpy – a framework for computer-aided borrowing detection}. Protolang 7, Düsseldorf, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {23-26 February 2021. \textit{Loanpy: A framework for computer-aided borrowing detection}. 43rd Annual Conference of the German Linguistic Society, Freiburg, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {19-22 November 2020. \textit{Towards a computer-aided framework for borrowing detection: Gothic loanwords in Hungarian?} 68. StuTS, Berlin, Germany}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {17-19 August 2020, \textit{Gothic-Hungarian lexical contacts}. Pre-Congress of Congressus XIII Internationalis Fenno-Ugristarum, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {1 July 2019, \textit{Gothic loanwords in Hungarian? Computational approaches to borrowing detection}. Fakultätsöffentliche Präsentation beim Dies Doctoralis der Philologisch-Kulturwissenschaftlichen Fakultät der Universität Wien, Vienna, Austria}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {6–8 June 2019, \textit{Hungaro-Gothica: Are there Gothic loanwords in Hungarian?} 3rd Budapest Linguistics Conference, Budapest, Hungary}
\end{cvpubs}

\begin{cvpubs}
    \cvpub {09-10 May 2019, \textit{Hungarian-Gothic contact?} Workshop der Sprachwissenschaftlichen DoktorandInnen der Wiener Germanistik and friends, Vienna, Austria}
\end{cvpubs}

%\begin{cvpubs}
%    \cvpub {PhD seminar uni helsinki may 2020}
%\end{cvpubs}

%-------------------------------------------------------------------------------